s.function

### 2022-06-05 src/s_la.Rmd
edits

library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  select(pcds, oa11cd, lsoa11cd, msoa11cd, ladcd, ladnm) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd
```

@@

df <- bind_rows(df9610, df1112) %>% 
  filter(
    V1.domain < m,             # for multiple pc
    #V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = n()) %>%            # for multiple pc  
  #summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

@@

@@

df.country %>% 
  ggplot(aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  geom_vline(xintercept = 2003) +
  ylab("N. of websites") +
  ggtitle("Country")
  #scale_x_date(breaks = df.test$year) 
```

@@

for (i in all.la){
  data <- df %>% filter(ladcd==i) %>%
    select(year, ladcd, n) 
    #lm(n~year, data = .)
    #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
  tryCatch(b.la <- tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
  tryCatch(a.la <-rbind(a.la,b.la), error=function(e) NULL)
}

a.la %>% filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  select(estimate) %>% 
  summarise(r = range(estimate),
            median = median(estimate))

a.la %>% filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  filter(p.value < 0.01) %>%    # (227759 - 212782)/227759  # 6% not sig 
  select(estimate) %>% 
  ggplot(aes(x=estimate)) + 
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = 2003, colour = "red")
  scale_x_continuous("year", labels = round(a$estimate, 0), breaks = round(a$estimate, 0)) 
  #scale_x_discrete(labels = as.factor(a$estimate))

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  filter(p.value < 0.01) %>%    # 376 / 376, all sig
  select(ladcd, estimate)
  #filter(estimate>2011)
```

@@

for (i in all.la){
  data <- df %>% filter(ladcd==i) %>%
    select(year, ladcd, n) 
    #lm(n~year, data = .)
    #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
  tryCatch(model <- (nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
  model.name <- paste0("model.", i)
  assign(model.name, model)
  tryCatch(b.la <- tidy(model), error=function(e) NULL)

@@

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  #mutate(estimate = round(estimate, 0)) %>% 
  #summarise(r = range(r2))
  filter(p.value < 0.01 & 
         r2 > 0.9) %>%    # 376 / 376, all sig, 330 r2 > 0.9
  select(ladcd, estimate, r2, std.error) %>%
  mutate(fast = ifelse(estimate < 2003, "fast", "slow"))

@@

for (i in all.la){
p <- ggplot(pred %>% left_join(a.la) %>% 
              filter(ladcd == i), aes(x = year, y = n, color = fast) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.test$year), breaks = df.test$year) +
  geom_vline(xintercept = pred %>% left_join(a.la) %>% filter(ladcd == i) %>% select(estimate) %>% first()) +
  ylab("N. of websites") + 
  labs(title = paste0(la@data %>% filter(LAD21CD== i) %>% select(LAD21NM) %>% first(), ", ", i)) +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"))

@@

```{r}
ggplot(a.la, aes(as.factor(round(estimate, 0)))) +
  geom_bar(fill = "#0073C2FF")
```

@@

```{r}
library(survival)

test.surv.data <- a.la %>% mutate(status = 1) %>% 
  left_join(data.la, by = c("ladcd" = "LAD21CD")) %>% 
  left_join(df %>% filter(year == 2012), by = "ladcd")

@@

Spatial data

@@

ggplot(data = la.f, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = fast)) + #fill = fast, 
  #theme_nothing(legend = TRUE) +
  labs(title = "Clusters") +
  geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
  #scale_fill_continuous(type = "viridis") +
  theme_void()

>>>>

library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)
library(survival)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  dplyr::select(pcds, oa11cd, lsoa11cd, msoa11cd, ladcd, ladnm) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd
```

@@

df <- bind_rows(df9610, df1112) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

@@

## Spatial data

@@

path.out <- paste0(path, "/outputs/s_uk.png")

df.country %>% 
  ggplot(aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  geom_vline(xintercept = 2003) +
  ylab("N. of websites") +
  ggtitle("S-curve, UK") +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(path.out)

  #scale_x_date(breaks = df.test$year) 
```

@@

for (i in all.la){
  data <- df %>% filter(ladcd==i) %>%
    dplyr::select(year, ladcd, n) 
    #lm(n~year, data = .)
    #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
  tryCatch(b.la <- tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
  tryCatch(a.la <-rbind(a.la,b.la), error=function(e) NULL)
}

a.la %>% filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  dplyr::select(estimate) %>% 
  summarise(r = range(estimate),
            median = median(estimate))

a.la %>% filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  filter(p.value < 0.01) %>%    # (227759 - 212782)/227759  # 6% not sig 
  dplyr::select(estimate) %>% 
  ggplot(aes(x=estimate)) + 
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = 2003, colour = "red") +
  #scale_x_continuous("year", labels = round(a$estimate, 0), breaks = round(a$estimate, 0)) +
  #scale_x_discrete(labels = as.factor(a$estimate))
  theme_minimal() +
  ggtitle("Counts of Xmid per year") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab("LAs") + xlab("year")

path.out <- paste0(path, "/outputs/xmid_f.png")
ggsave(path.out)

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  filter(p.value < 0.01) %>%    # 376 / 376, all sig
  dplyr::select(ladcd, estimate)
  #filter(estimate>2011)
```

@@

for (i in all.la){
  data <- df %>% filter(ladcd==i) %>%
    dplyr::select(year, ladcd, n) 
    #lm(n~year, data = .)
    #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
  tryCatch(model <- (nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
  model.name <- paste0("model.", i)
  assign(model.name, model)
  tryCatch(b.la <- tidy(model), error=function(e) NULL)

@@

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  #mutate(estimate = round(estimate, 0)) %>% 
  #summarise(r = range(r2))
  filter(p.value < 0.01 & 
         r2 > 0.9) %>%    # 376 / 376, all sig, 330 r2 > 0.9
  dplyr::select(ladcd, estimate, r2, std.error) %>%
  mutate(fast = ifelse(estimate < 2003, "fast", "slow"))

@@

for (i in all.la){
p <- ggplot(pred %>% left_join(a.la) %>% 
              filter(ladcd == i), aes(x = year, y = n, color = fast) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df$year), breaks = df$year) +
  geom_vline(xintercept = pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()) +
  ylab("N. of websites") + 
  labs(color = "Website \ndiffusion speed") +
  labs(title = paste0(la@data %>% filter(LAD21CD== i) %>% dplyr::select(LAD21NM) %>% first(), ", ", i)) +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = 2003, colour="grey30", linetype="dashed")

@@

**TO DELETE**, done it above.

```{r, eval=F}
# path.out <- paste0(path, "/outputs/xmid_f.png")
# 
# ggplot(a.la, aes(as.factor(round(estimate, 0)))) +
#   geom_bar(fill = "#0073C2FF") +
#   theme_minimal() +
#   ggtitle("Counts of Xmid per year") +
#   theme(plot.title = element_text(hjust = 0.5)) +
#   ylab("LAs") + xlab("year") 
# 
# ggsave(path.out)
```

@@

using `library(survival)`

```{r}
test.surv.data <- a.la %>% mutate(status = 1) %>% 
  left_join(data.la, by = c("ladcd" = "LAD21CD")) %>% 
  left_join(df %>% filter(year == 2012), by = "ladcd")

@@

@@

path.out <- paste0(path, "/outputs/speed_pam.png")
ggplot(data = la.f, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = fast)) + #fill = fast, 
  scale_fill_manual(values = c("darkorchid3", "orange"), #darkmagenta, purple4
                    na.value = "grey70") +

  #theme_nothing(legend = TRUE) +
  labs(title = "Website diffusion speed in Local authorities") +
  geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
  geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
  #scale_fill_continuous(type = "viridis") +
  labs(fill='Diffusion') +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
```

### 2022-06-05 src/s_oa.Rmd
edits

@@

```{r}
df.test <- df %>% filter(oa11cd == "S00103828")

@@

```{r}
a <- as_tibble()
all.oa <- unique(df$oa11cd)
for (oa in all.oa){
  data <- df %>% filter(oa11cd==oa) %>%
    select(year, oa11cd, n) 
    #lm(n~year, data = .)
    #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
  tryCatch(b <- tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
  tryCatch(a <-rbind(a,b), error=function(e) NULL)
}

a %>% filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  select(estimate) %>% 
  summarise(r = range(estimate))

a %>% filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  filter(p.value < 0.01) %>%    # (227759 - 212782)/227759  # 6% not sig 
  select(estimate) %>% 
  ggplot(aes(x=estimate)) + 
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = 2003, colour = "red")
  scale_x_continuous("year", labels = round(a$estimate, 0), breaks = round(a$estimate, 0)) 
  #scale_x_discrete(labels = as.factor(a$estimate))

@@

```{r}
path.out <- paste0(path, "/data/temp/s.csv")
write_csv(a, path.out)
```

@@

oa.gb.f <- oa.gb.f %>% left_join(a, by = "id") %>% 
  mutate(fast = ifelse(estimate < 2003, "fast", "slow")) %>% 
  arrange(order)  # if i don't order merge.nuts.f loses order and the map has gaps

# oa.gb.f %>% mutate(fast = ifelse(estimate < 2003, 1, 0)) %>% 
#   arrange(order) %>% 
ggplot(data = oa.gb.f %>% arrange(order), aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = estimate)) + #fill = fast, 
  #theme_nothing(legend = TRUE) +
  labs(title = "Clusters") +
  scale_fill_continuous(type = "viridis") +
  theme_void()
```

@@

oa.class.df <- a %>%  
  mutate(fast = ifelse(estimate < 2003, "fast", "slow")) %>% 
  left_join(oa.class@data, by = c("id"="OA_SA")) %>% 
  select(1:10) %>% 
  arrange(id)

@@

oa.class.df %>% 
  filter(fast == "slow") %>% 
  group_by(SUBGRP) %>% 
  summarise(n=n()) %>% 
  arrange(-n) %>% 
  mutate(freq = n / sum(n),
         freq = round(freq, 2),
         cum.n = cumsum(n),
         cum.freq = cumsum(n / sum(n)),
         cum.freq = round(cum.freq, 2)) %>% 
  left_join(pen %>% select(code, name),
            by = c("SUBGRP" = "code")) %>% 
  kable()

@@

# Join with distance and area
oa.class.df <- oa.class.df %>% left_join(dist, by = c("id" = "oa11cd")) 
sapply(df, function(x) sum(is.na(x)))
```

@@

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% select(oa11cd, dist.retail)

# Join with complete panel
oa.class.df <- oa.class.df %>% left_join(dist.retail, by = c("id" = "oa11cd"))

@@

oa.class.df <- oa.class.df %>% left_join(df %>% group_by(oa11cd) %>% summarise(max.n = max(n, na.rm = T)), #filter(year==2012), 
                          by = c("id"="oa11cd"))

@@

model <- lm(estimate ~ log(London + 1) + log(dist + 1) + log(dist.retail + 1) + 
              as.factor(SPRGRP) + log(POPULATION) + max.n, data = oa.class.df) #%>%filter(estimate>1996 & estimate <2012)
summary(model)
nobs(model)

>>>>

I re-run the below using a `foreach` loop. It created a new object `a_` with c. 40k
rows. Once I filter the old `a` object derived from the `for` loop I have c. 60k rows.
I run `lm' and `coxph` using both and the results are not strong not easy to interpret.

The `/data/temp/s_oa.csv` is based on the `for` loop.

@@

```{r}
df.test <- df %>% filter(oa11cd == "E00138496")

@@

```{r}
# a <- as_tibble()
# all.oa <- unique(df$oa11cd)
# #for (oa in all.oa){
# a <- foreach(oa = all.oa, .combine = 'rbind',
#              #.final =  function(x) setNames(x, names(all.oa)),
#           .packages = c("tidyverse",
#                                     "broom")) %dopar% {
#   data <- df %>% filter(oa11cd==oa) %>%
#     dplyr::select(year, oa11cd, n) 
#     #lm(n~year, data = .)
#     #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
#   tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
#   #tryCatch(a <-rbind(a,b), error=function(e) NULL)
# }

# Setup cluster
# https://www.blasbenito.com/post/02_parallelizing_loops_with_r/
n.cores <- parallel::detectCores() - 1
my.cluster <- parallel::makeCluster(
  n.cores, 
  type = "PSOCK"
  )
print(my.cluster)
doParallel::registerDoParallel(cl = my.cluster)
foreach::getDoParWorkers()

a <- foreach(oa = all.oa, .combine = 'rbind', .packages = c("tidyverse",
                           "broom")) %dopar% 
  {
    data <- df %>% filter(oa11cd==oa) %>%
    dplyr::select(year, oa11cd, n) 
    tryCatch(model <- tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)

    tryCatch(model <- model %>% dplyr::filter(term == "xmid"), error=function(e) NULL)

    c(oa, model)
    }

stopCluster(my.cluster)

# drop the second duplicates  
a_ <- as.data.frame(a) %>% 
  rename(oa11cd = V1) %>% 
  #mutate(help = duplicated(estimate))
  distinct(estimate, std.error, statistic, p.value, .keep_all = TRUE) %>% 
  unnest()

a_ %>% #filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  dplyr::select(estimate) %>% 
  summarise(r = range(estimate))

a_ %>% #filter(term=="xmid") %>% 
  mutate(estimate = round(estimate, 0)) %>% 
  filter(p.value < 0.01) %>%    # (227759 - 212782)/227759  # 6% not sig 
  dplyr::select(estimate) %>% 
  ggplot(aes(x=estimate)) + 
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = 2003, colour = "red")
  scale_x_continuous("year", labels = round(a$estimate, 0), breaks = round(a$estimate, 0)) 
  #scale_x_discrete(labels = as.factor(a$estimate))

a_ %>% filter(estimate<1996)

@@

```{r}
path.out <- paste0(path, "/data/temp/s_oa.csv")
write_csv(a, path.out)
```

@@

oa.gb.f <- oa.gb.f %>% left_join(a_, by = c("id"="oa11cd")) %>% 
  mutate(fast = ifelse(estimate < 2003, "fast", "slow")) %>% 
  arrange(order)  # if i don't order merge.nuts.f loses order and the map has gaps

# oa.gb.f %>% mutate(fast = ifelse(estimate < 2003, 1, 0)) %>% 
#   arrange(order) %>% 
ggplot(data = oa.gb.f %>% arrange(order) %>% filter(estimate<2020 & estimate >1996), aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = estimate)) + #fill = fast, 
  #theme_nothing(legend = TRUE) +
  labs(title = "Clusters") +
  scale_fill_continuous(type = "viridis") +
  theme_void()
```

@@

oa.class.df <- a_ %>%  
  mutate(fast = ifelse(estimate < 2003, "fast", "slow")) %>% 
  left_join(oa.class@data, by = c("oa11cd"="OA_SA")) %>% 
  dplyr::select(1:14) %>% 
  arrange(oa11cd)

@@

oa.class.df %>% 
  filter(fast == "fast") %>% 
  group_by(SUBGRP) %>% 
  summarise(n=n()) %>% 
  arrange(-n) %>% 
  mutate(freq = n / sum(n),
         freq = round(freq, 2),
         cum.n = cumsum(n),
         cum.freq = cumsum(n / sum(n)),
         cum.freq = round(cum.freq, 2)) %>% 
  left_join(pen %>% dplyr::select(code, name),
            by = c("SUBGRP" = "code")) %>% 
  kable()

@@

# Join with distance and area
oa.class.df <- oa.class.df %>% left_join(dist, by = c("oa11cd" = "oa11cd")) 
sapply(df, function(x) sum(is.na(x)))
```

@@

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% dplyr::select(oa11cd, dist.retail)

# Join with complete panel
oa.class.df <- oa.class.df %>% left_join(dist.retail, by = c("oa11cd" = "oa11cd"))

@@

oa.class.df <- oa.class.df %>% left_join(df %>% group_by(oa11cd) %>% summarise(max.n = max(n, na.rm = T)), #filter(year==2012), 
                          by = c("oa11cd"="oa11cd"))

@@

model <- lm(estimate ~ log(London + 1) + log(dist + 1) + log(dist.retail + 1) + 
              as.factor(SPRGRP) + log(POPULATION) + max.n, data = oa.class.df %>% filter(estimate>1996 & estimate <2012))
summary(model)
nobs(model)

oa.class.df <- oa.class.df %>% mutate(status = 1)

cf <- coxph(Surv((estimate-1996), status) ~ log(London + 1) + log(dist + 1) + log(dist.retail + 1) + 
              as.factor(SPRGRP) + log(POPULATION) + max.n, data = oa.class.df %>% filter(estimate>1996 & estimate <2012)) #, weights = 1/(std.error)^2)
summary(cf)
